\LARGE \bf Mean Estimation from One-Bit Measurements

### 2021-10-25 response.tex

\subsection*{Summary of the Review by AE Tyagi}
The first reviewer has asked further clarification about the proofs. I, too, think that more details about the proof are needed. The second reviewer has raised questions concerning extensions to more general settings, perhaps requiring further elaboration on the limitation of the approach. Since both reviewers have requested revision, I think it is important that the authors address their concerns in a rebuttal and provide the required details.

\begin{response}
Thank you for handling the paper and for obtaining two excellent reviews. We addressed all reviewers' comments as explained below, with particular attention to the proofs and the extension to more general settings. 
\end{response}

\subsection*{Response to comments by Reviewer 1}
\begin{review}
(1) My main concern is with Theorem 3(ii) -- if I understand correctly, the proof given does not quite prove the statement. In particular, the statement says that the limiting distribution is normal with mean 0, whereas the proof (Lemma 14) says that it is normal with mean h. If the mean indeed depends on h, then the estimator is not regular (Definition 1) and so the statement about the estimator attaining local asymptotic minimaxity in Theorem 3(ii) becomes dubious.
\end{review}

\begin{response}
We greatly appreciate the reviewer's overall through work and in particular for bringing the issue with the proof of Theorem 3 to our attention. As it turns out, one of the equations in the proof was incorrect because it indicated a location shift by $h$ in both sides of the equation instead of only in one side as per the definition of a regular estimator. We fixed this issue by changing Lemma 14 to the following from.
\setcounter{thm}{13}
\begin{lemma} 
  Let $h_n \to h \in \R$, and define $P_{n,h} = P_{\theta + h_n / \sqrt{n}}^n$.
  Then 
  \begin{align}
    \sqrt{n}\left( \bar{\theta}_n - \theta \right)
    \mathop{\cd}_{P_{n,h}}
    \normal\left( h,\frac{1}{4 f(0)^2}\right).
  \end{align}
\end{lemma}
%The new notation is in accordance with \cite[Ch. 7]{van2000asymptotic}. 
\end{response}

@@

\begin{review}
(2) I think there are problems with the example in Appendix VII that demonstrates fast convergence in the case of uniform distribution. The initial estimate $\theta^{init}$ is set to be the maximal threshold for which $B_i$ = 0 for all observations corresponding to that threshold. But the way $B_i$ is defined, wouldn't this maximal threshold always be the very last threshold in the interval $[-n \epsilon, n \epsilon]$? If, instead, we interchange the roles of $0$ and $1$ in the defining $B_i$, then we might be on to something. But then, what confuses me is the statement: ``we always have $\theta^{init} \geq \theta - (2n\epsilon)/m$''; which is not true (since $\theta$ is the median of the distribution, and not the left-end point). Ok, this can be salvaged by saying that $\theta^{init}$ is estimate of the left-end point (i.e. $\theta - 1$). But then again, the confusion arises in the next line: ``The event $\theta^{init} \geq t_j* + (2n\epsilon)/m$ may occur only if for each of the $n/m$ observations in the set $I_{j^\star+1}...$''. Why ``only if''? It may well be that we observe both $0$ and $1$ for observations in $I_{j^\star+1}$ and observe only $0$'s in $I_{j^\star+2}$; this would also make the event ``$\theta^{init} \geq t_j^\star + (2n\epsilon)/m$'' happen.
\end{review}

\begin{response}
We thank Reviewer 1 for pointing on the problems with this example which indeed was missing a key ingredient: a comparison between our communication-limited estimator to the maximum of the samples within a bin. We have carefully went through this example and revised to add the missing part and resolve all other issues.

We refer the reviewer to the revised manuscript for reviewing these changes; we highlighted in blue the parts that went through significant changes.

@@

\end{response}

\begin{review}
\begin{enumerate}
\item  Section III A, page 8: Extra braces in the indicator function in the definition of $B_i$ and the line after that.
\begin{response}
Fixed. 
\end{response}

\item Section III B, page 9, equation (7): Why is it $O(1/n)$? In the proof (Appendix VII A), $D*$ has $o(1/n)$; so after multiplication by $n$, we get $o(1)$. Could you clarify what $o(1/n)$ is hiding that makes it $O(1/n)$ in (7) instead of merely $o(1)$?

\begin{response}
Thank you for this comment. It made us realized that there was a mistake in the proof of Proposition~1: we should have replaced the $o(1/n)$ term with $O(n^{-2})$. We now provide a more detailed derivation of the expansion of $D^\star$ as $n\to \infty$ that provides the second order term. The relevant part is as follows.

\begin{quote}
Denote by $D^\star$ the optimal MSE in the Gaussian CEO with $L$ observers and under a total sum-rate $r = r_1 + \ldots +r_L$. An expression for $D^\star$ as a function of $r$ is give as \cite[Eq. 10]{chen2004upper}:
\begin{equation} \label{eq:ceo_optimal_sumrate}
r = \frac{1}{2} \log^+ \left[ \frac{\sigma_\theta^2}{D^\star} \left( \frac{D^\star L}{ D^\star L - \sigma^2 + D^\star \sigma^2 / \sigma_\theta^2 }\right)^L  \right].
\end{equation}
For the special case where $r = n$ and $L=n$, we have
\begin{equation} \label{eq:ceo_optimal_sumrate2}
n = \frac{1}{2} \log_2 \left[ \frac{\sigma_\theta^2}{D^\star} \left(\frac{ D^\star n }{D^\star n - \sigma^2 + D^\star \sigma^2/\sigma_\theta^2 }  \right)^n  \right].
\end{equation}
Consider the distributed encoding setting (iii) in the case where $f(x) = \Ncal(0,\sigma^2)$ and the prior on $\Theta$ is $\pi = \Ncal(0,\sigma_\theta^2)$. The Gaussian CEO problem of \cite{viswanathan1997quadratic} with a unit bitrate $r_1=\ldots = r_n =1$ at each terminal and blocklength $k=1$ reduces to our distributed setting (iii). Since $D^\star$ satisfying \eqref{eq:ceo_optimal_sumrate2} describes the MSE in the CEO setting under an optimal allocation of the sum-rate $r = n$ among $n$ encoders, it provides a lower bound to the minimal MSE in estimating $\theta$ in the distributed setting.

By noting that $1/D^\star$ grows no faster than a polynomial in $n$ \cite{viswanathan1997quadratic}, we rely on the expansion
\begin{align*}
\left(\frac{\sigma_{\theta}^2}{D^\star}\right)^{1/n} 
= 1 + \frac{\log \left(\frac{\sigma_{\theta}^2}{D^\star}\right)}{n}+\frac{\log^2\left(\frac{\sigma_{\theta}^2}{D^\star}\right)}{2 n^2}+O\left(n^{-3}\right),
\end{align*}
to obtain that, in limit $n\rightarrow \infty$, \eqref{eq:ceo_optimal_sumrate2} behaves as 
\begin{align*}
D^\star = 
\frac{4 \sigma^2}{3 n}
+ \frac{16 \sigma^2}{9 n^2 \sigma_{\theta}^2 }-\frac{4 \sigma^2 \log \left(\frac{\sigma_{\theta}^2}{D^\star}\right)}{9 n^2}
+O(n^{-3}).
\end{align*}
\end{quote}
\end{response}

\item Section IV B, page 13, line 3: It says $B_i$ a.s. converges to $F(\theta_0 - \theta)$. Shouldn't it say $E[B_i] = F(\theta_0 - \theta)$?
\begin{response} Thank you. It should say $E[B_i] = F(\theta_0 - \theta)$. We fixed this issue. 
\end{response}

@@

\item Section V, page 15, Assumption A2(ii): The subscript in $A_n$ and $k_n$ should be "$i$" and not "$n$".
\begin{response} Fixed.
\end{response}

\item Section V A, page 17, line 3: In "...ML estimator attains the local asymptotic MSE of Theorem 2", it should be "Theorem 6" instead of "Theorem 2".
\begin{response} Fixed.
\end{response}

\item Section V B, page 17, second line in the subsection: In "...density of the threshold values that maximizes the worst-case information $\inf_\theta \kappa(\theta) = \kappa_\lambda(\theta)$...", it seems to say that "$\inf_\theta \kappa(\theta) = \kappa_\lambda(\theta)$", whereas I think what the authors mean is "$\kappa(\theta) = \kappa_\lambda(\theta)$". Better phrasing required.
\end{enumerate}

\begin{response}
We thank the reviewer for bringing it to our attention that the notation here is unclear. We rewritten the relevant part as follows. 
\begin{quote}
    We conclude this section by considering the \newtext{distribution} of the threshold values
that maximizes the worst-case information $\inf_\theta \kappa(\theta)
= \kappa_\lambda(\theta)$ where $\kappa_\lambda(\theta)
= \int \eta(t - \theta) \lambda(dt)$.
The \newtext{optimal distribution $\lambda^\star$} solves the
optimization problem
\begin{align*}
  \begin{split}
    \mathrm{maximize} \quad &  \inf_{\theta \in \Theta} \int \eta(t-\theta) \lambda(dt)
    \\ 
    \mathrm{subject~to} 
    \quad & \lambda(dt)\geq 0,\quad \int \lambda(dt) \leq 1. 
  \end{split}
\end{align*}
\end{quote}
\end{response}

@@

\begin{enumerate}
    \item Appendix VII, page 20, line after equation (19): Instead of $\sqrt{2 \log n}$, should it be $(8 \log n)$?
\begin{response}
Yes. Thank you for catching this. 
\end{response}

\item Appendix VIII, page 22, second line of Lemma 10: Should say "Assumption A1" instead of "Assumption 1".
\begin{response}
Fixed.  
\end{response}

\item Appendix VIII, page 23, proof of Lemma 10, line after equation defining A: It says "$t_1^+ \leq t_k^+ \leq \infty$", which is technically true, but it might be better to insert ellipsis and write "$t_1^+ \leq ... \leq t_k^+ \leq \infty$".

\begin{response}
We agree. We have fixed this isssue according to the Reviewer's suggestion. 
\end{response}

@@

\item Appendix IX B, page 31, line after equation (37): the quantity "delta-bar" should have subscript "n" instead of "i".
\begin{response}
Fixed.
\end{response}

\item Appendix IX B, page 31, Corollary 15, condition (ii): In the definition of the Fisher information $I_h$, the expectation should have subscript "h" instead of "theta".
\begin{response}
Fixed.
\end{response}

\item Appendix IX C, page 32, last line of Appendix IX C: Could you clarify what you mean by "a finite approximation to the prior measure $\pi$"?

\begin{response}
We added the assumption that $\pi$ has a finite second moment and revised this part accordingly without 
using a finite approximation to the prior measure $\pi$. 
\end{response}

@@

\end{review}

\subsection*{Response to comments by Reviewer 2}
%My main comments are below.
\begin{itemize}
    \item For the lower bound on non-adaptive estimators, is it possible to characterize the worst-case gap between the efficiency of a non- adaptive estimator and the best rate for an adaptive estimator (possibly in terms of the diameter of the parameter space or variance of the density)? This will give a more quantitative view of the separation between adaptive and non-adaptive estimators.

    \begin{response}
    We thank the Reviewer for raising this interesting point. We should first clarify that our results in the distributed encoding setting provides the asymptotic relative efficiency only when the estimator is based on thresholds detectors, in which case this efficiency depends on the density of the thresholds. 
    Under this setting, it appears to us that Fig. 6 provides a characterization of the efficiency gap similarly to the one proposed by the reviewer, at least in the special case in which the samples are normally distributed and the threshold density is either uniform or obtained as the solution of the optimization problem (17).

    The Reviewer's comment made us realize that we initially did not explain well that our results in Section V-C yields the exact efficiency gap under distributed threshold encoding. To improve this point, we revised Figure 6 as follows. 
    \begin{quote}
\begin{figure}[h!]
  %%%%% COMMENTED TIKZ PICTURE %%%%%
  \begin{center}
\begin{tikzpicture}[scale = 1]
\begin{axis}[
width=8cm, height=6cm,
xmin=.03,
xmax=2.5, 
xmode = log,
restrict y to domain = 0:100,
ymin = 0,
ymax = 1,
samples=1, 
xlabel= {$\sigma$},
%xtick={-0.5,0,0.5},
%xticklabels={-$$, 0, $b$},
ytick={0,0.637,1},
yticklabels={0,$\frac{2}{\pi}$,1},
ylabel = {\scriptsize Relative Efficiency},
line width=1.0pt,
mark size=1.5pt,
ymajorgrids,
xmajorgrids,
legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
]
\addplot[color = red, smooth,
line width=1.0pt,
%mark size=1.5pt,mark=x,
] plot table [x = x, y = y, col sep=comma] {./Figs/minmax_ARE_b0.5.csv};
\addlegendentry{\scriptsize optimal threshold density};

\addplot[color = black!35!green, dashed, line width=1.0pt,
        %mark size=1.5pt, mark=^
        ]
 plot table [x = x, y = z, col sep=comma] {./Figs/minmax_ARE_b0.5.csv};
\addlegendentry{\scriptsize uniform threshold desnity};

\addplot[color = black, smooth, dotted, line width = 1pt] 
coordinates {
            (0.03, .637) (10, .637)
            };
\addlegendentry{\scriptsize attained in the adaptive case};
%\draw[->] (axis cs:0.1,.5) -- node[below, align=center] {\scriptsize ARE attained in \\ \scriptsize the adaptive case} (axis cs:0.1, .63);
\end{axis}
\end{tikzpicture}

\setcounter{figure}{5}
\caption{
\newtext{
Minimax relative efficiency under distributed encoding. ARE versus $\sigma$ for $f(x)$ the standard normal density with variance $\sigma^2$ and parameter space $\Theta = [-1/2,1/2]$. The dashed curve (green) is the ARE under a uniform threshold density over $\Theta$ given by $K_{\unif}\sigma^2$ of (19). 
The line $\pi/2$ is attained under adaptive encoding uniformly over the parameter space for any $\sigma$.}}
\end{center}
\end{figure}

\end{quote}

@@

    \end{response}
\item The setting of one-dimensional distribution and one-bit messages is a bit limited. How does the technique of the paper generalize to higher dimensions or higher communication budget (more bits from each user)? The result will be stronger if more general results can be provided.

\begin{response}
We agree that the extension of the setting of the paper to higher dimensions is an excellent point for discussion and probably for a future work. We thank the reviewer for proposing it.

Arguably, there are several ways to generalize our setting to higher dimension and higher communication budgets. Many of these generalizations falls under the settings discussed in 
\cite{zhang2013information,shamir2014fundamental,braverman2016communication,han2018geometric,barnes2020lower}, although these references do not yield the asymptotic relative efficiency (ARE) but only characterization of the way the error scales in the communication bit-budget and the dimension. It is still unclear whether we can extend our methods to derive the ARE for any dimension and bit budget, but anyway such extension is not straightforward so we decided to leave this extension as a future work. 
%characterizing the way the error scales with the number of bits and the dimension and not on the exact asymptotic efficiency. 
%
%Indeed, it seems challenging to derive the exact efficiency in higher dimensions and communication bit budgets. To illustrates a possible source for this challenge, consider a known symmetric base distribution $F$ over $\reals^k$ and the problem of estimating the shift $\theta \in \reals^k$ of a sequence of samples from the shifted $F$ with $b$ bits per round of communication. The following estimation and quantization scheme is proposed to outperform a naive tenderized scheme: construct a $b$-bit optimal vector quantizer matching to $F$. Namely, dissect $\reals^k$ into $b$ regions in a way that the MSE obtained between a sample from $F$ and the center of mass of $F$ over the region where the sample falls is minimal across all possible dissections. The Lloyd algorithms provides an iterative method of approximating such optimal quantizer. The estimation-encoding scheme is as follows: Given an estimate $\theta_{i-1}$, and an expected error $\sigma_{i-1}$, and a new observation $X_i \in \reals^k$, send the index of the region in $\reals^k$ where $X_i/\sigma_{i-1}$ falls. The estimation $\theta_i$ is the center of mass of this region. This method is expected to...
Consequently, we added the following paragraph to the Conclusions: 
\begin{quote}
    Natural extensions of the setting of this work include situations when the communication bit-budget $b$ is larger than one and when each sample is a $d$-dimensional vector. Rough lower bounds on the MSE for this general case follows from several recent works (e.g. \cite{zhang2013information,shamir2014fundamental,braverman2016communication,han2018geometric,barnes2020lower}), that in particular imply that in some cases the MSE scales in the regular parametric rate of $1/n$ when $b$ and $d$ are held fixed in the sample size $n$. Nevertheless, the coefficient of the leading scaling term corresponding to the ARE is still unknown; deriving the ARE for general $b$ and $d$ is left as a future challenge.
\end{quote}

### 2021-10-25 conclusions.tex
finished response and revision

\section{Conclusions \label{sec:conclusions}}
We considered the risk and efficiency in estimating the mean of a symmetric and log-concave distribution from a sequence of bits, where each bit is obtained by encoding a single sample from this distribution. 
%
In an adaptive encoding setting, we showed that, asymptotically, no estimator can be more efficient than the median of the samples. We also showed that this bound is tight by presenting two adaptive encoding and estimation procedures that are as efficient as the median. Furthermore, we showed that only one round of adaptivity is required to attain optimal efficiency. In the distributed setting we provided conditions for local asymptotic normality of the encoded samples, which implies asymptotic minimax bound on both the risk and efficiency relative to the mean. 
%
Under local asymptotic normality, the optimal estimation performance derived for the adaptive case can only be attained over a finite number of points, i.e., no scheme is uniformly optimal in this setting. 
%
We further considered the special case where the sequence of bits is obtained in a distributed manner by comparing against a prescribed sequence of thresholds. We characterized the performance of the optimal estimator from such bit-sequence using the density of the thresholds and considered the density that minimizes the minimax risk. 
%
%\par
%Obvious extensions of our work include deriving explicit bounds and optimal procedures when more than one-bit per sample is provided or when each sample is a vector. Another possible extension may consider the efficiency of estimation when single bits are sent between nodes of a directed graph.

>>>>

\section{Conclusions \label{sec:conclusions}}
We considered the risk and efficiency in estimating the mean of a symmetric and log-concave distribution from a sequence of bits, where each bit is obtained by encoding a single sample from this distribution. 
%
In an adaptive encoding setting, we showed that, asymptotically, no estimator can be more efficient than the median of the samples. We also showed that this bound is tight by presenting two adaptive encoding and estimation procedures that are as efficient as the median. Furthermore, we showed that only one round of adaptivity is required to attain optimal efficiency. In the distributed setting we provided conditions for local asymptotic normality of the encoded samples, which implies asymptotic minimax bound on both the risk and efficiency relative to the mean. 
%
Under local asymptotic normality, the optimal estimation performance derived for the adaptive case can only be attained over a finite number of points, i.e., no scheme is uniformly optimal in this setting. 
%
We further considered the special case where the sequence of bits is obtained in a distributed manner by comparing against a prescribed sequence of thresholds. We characterized the performance of the optimal estimator from such bit-sequence using the density of the thresholds and considered the density that minimizes the minimax risk. 
%
%\par

\newtext{
Natural extensions of this work include situations when the communication bit-budget $b$ is larger than one and when each sample is a $d$-dimensional vector. Rough lower bounds on the MSE for this general case follows from several recent works (e.g. \cite{zhang2013information,shamir2014fundamental,braverman2016communication,han2018geometric,barnes2020lower}), that in particular imply that in some cases the MSE scales in the regular parametric rate of $1/n$ when $b$ and $d$ are held fixed in the sample size $n$. Nevertheless, the coefficient of the leading $1/n$ term corresponding to the ARE, which we characterized here in the case $b=1$and $d=1$, is still unknown in the general case.}

### 2021-10-25 distributed-estimation.tex
finished response and revision

Theorem~\ref{theorem:non-adaptive-minimax} shows that the limiting variance
term $\kappa(\theta)$ provides strong lower bounds on the efficiency of any
non-adaptive estimator, and moreover, that these bounds necessarily depend
on $\theta$. This suggests that attaining any type of good (uniform)
efficiency with non-adaptive estimators will be challenging.  As a
particular consequence, for the squared error $L(x) = x^2$, for any $\delta
> 0$ and $\theta$, there exists a $c < \infty$ such that $\sup_{|\tau -
  \theta| \le c / \sqrt{n}} \E_\tau[(\theta_n - \tau)^2] \ge \frac{(1 -
  \delta)}{n \kappa(\theta)} + o(1/n)$.

@@

We now consider a restricted case where each detection region is a
half-open interval, i.e., the $i$th message is obtained by comparing $X_i$
against a single threshold. Under the adaptive signal acquisition,
this is sufficient for asymptotic optimality;
in non-adaptive settings, it is not sufficient, though we may characterize
a few additional optimality results.
%% As we explain next, the existence of a density
%% for the sequence of thresholds is enough to establish local asymptotic
%% normality and leads to a closed-form expression for the precision parameter
%% and the ARE.
Assume now that each $B_i$ is of the form
\begin{equation}
  \label{eq:threshold_message}
  B_i = \sgn(t_i - X_i) = \begin{cases} 1 & X_i<  t_i, \\
    -1 & X_i \geq t_i,
  \end{cases}  
\end{equation}
where $t_i\in\mathbb R$ is the \emph{threshold} of the $i$th encoder. In
other words, the detection region of $B_i$ is $A_i = (t_i,\infty)$ and
$\mathbb P(X_i \in A_i) = F \left( B_i(t_i-\theta) \right)$. It follows that
\begin{equation}
  L_n(A_1,\ldots,A_n;\theta)
  = \frac{1}{n} \sum_{i=1}^n \frac{ \left(f(t_i-\theta) \right)^2 }{F\left(t_i-\theta \right) F\left(\theta - t_i \right) }  = \frac{1}{n} \sum_{i=1}^n \eta(t_i - \theta).
  \label{eq:Ln_threshold}
\end{equation}
A natural condition for the existence of the limit \eqref{eq:Ln_threshold}
as $n\to \infty$ is that the empirical distribution of the threshold values
converges to a probability measure. Specifically, for an interval $I \subset
\mathbb R$, define
\begin{equation*}
  \lambda_n(I) = \frac{ \card \left( I \cap \{t_1,t_2,\ldots \} \right)}{n}. 
\end{equation*}
Then an investigation of the proof of
Theorem~\ref{theorem:non-adaptive-minimax} in
Section~\ref{sec:proof-non-adaptive-minimax}, specifically
Sec.~\ref{sec:proof-lan-bits} and the bounds~\eqref{eqn:h-fourth}, show that
as $\eta(t) \le \eta(0)$ for all $t \in \R$ under
Assumption~\ref{assump:failure_rate}, the following corollary follows. (The
corollary relies on local asymptotic normality~\cite[Ch.~7]{VanDerVaart98};
see Appendix~\ref{sec:proof-sgd-regular} for some brief discussion of such
conditions.)
\begin{cor} \label{cor:LAN_thresh}
  Let $\{t_n\}_{n=1}^\infty$ be a sequence of threshold values such that
  $\lambda_n$ converges (weakly) to a probability measure $\lambda$ on
  $\mathbb R$. Then the conclusions of
  Theorem~\ref{theorem:non-adaptive-minimax} apply with
  %% $\left\{ B_i = \sgn(X_i - t_i) \right\}_{i=1}^n$ is a
  %% LAN family with precision parameter
  \begin{equation*}
    \kappa(\theta) = \int_{\mathbb R} \eta(t-\theta) \lambda(dt). 
  \end{equation*}
  Moreover, the family of laws of $\{B_i = \sgn(X_i - t_i)\}_{i = 1}^n$
  under $\{P_\theta\}_{\theta \in \Theta}$ is locally asymptotically normal
  with information $\kappa(\theta)$.
\end{cor}

@@

By Assumption~\ref{assump:failure_rate},
$\eta(x)$ attains its maximum at the origin, so we conclude that
\begin{equation*}
  \kappa(\theta) \leq \sup_{t\in \mathbb R} \eta \left( t-\theta\right) = \eta(0).
\end{equation*}
Moreover, this upper bound on $\kappa(\theta)$ is attained only when
$\lambda$ is the point mass at $\theta$. Since $\theta$ is \emph{a priori}
unknown, we conclude that estimation in the distributed setting using
threshold detection is strictly suboptimal compared to the adaptive
setting; the ability to choose the thresholds $t_i$
adaptively conditional on previous messages is necessary for optimal
efficiency.

@@

\begin{figure}
  %%%%% COMMENTED TIKZ PICTURE %%%%%
  \begin{center}
\begin{tikzpicture}[scale = 1]
\begin{axis}[
width=8cm, height=6cm,
xmax=2.5, 
xmode = log,
restrict y to domain = 0:100,
ymin = 0,
ymax = 1,
samples=1, 
xlabel= {$\sigma$},
%xtick={-0.5,0,0.5},
%xticklabels={-$$, 0, $b$},
ytick={0,0.637,1},
yticklabels={0,$2/\pi$,1},
ylabel = {\scriptsize Relative Efficiency},
line width=1.0pt,
mark size=1.5pt,
ymajorgrids,
xmajorgrids,
legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
]
\addplot[color = red, smooth, line width = 1pt] plot table [x = x, y = y, col sep=comma] {./Figs/minmax_ARE_b0.5.csv};
\addlegendentry{optimal threshold density};

\addplot[color = black!35!green, smooth, dashed, line width = 1pt] plot table [x = x, y = z, col sep=comma] {./Figs/minmax_ARE_b0.5.csv};
\addlegendentry{uniform threshold desnity};
\end{axis}
\end{tikzpicture}
\caption{\label{fig:minimax_ARE} 
Minimax relative efficiency under distributed encoding. ARE versus $\sigma$ for $f(x)$ the standard normal density with variance $\sigma^2$ and $\Theta = [-1/2,1/2]$. The dashed curve (green) is the ARE under a uniform threshold density over $\Theta$ given by $K_{\unif}\sigma^2$ of \eqref{eq:uniform_risk}. \newtext{
The line $\pi/2$ is the optimal relative efficiency, attained under adaptive encoding for any $\sigma$ uniformly over the parameter space.}}
\end{center}
\end{figure}

>>>>

Theorem~\ref{theorem:non-adaptive-minimax} shows that the limiting variance
term $\kappa(\theta)$ provides a strong lower bound on the efficiency of any
non-adaptive estimator, and moreover, that this bound necessarily depends
on $\theta$. As a
particular consequence, for the squared error $L(x) = x^2$, for any $\delta
> 0$ and $\theta$, there exists a $c < \infty$ such that $\sup_{|\tau -
  \theta| \le c / \sqrt{n}} \E_\tau[(\theta_n - \tau)^2] \ge \frac{(1 -
  \delta)}{n \kappa(\theta)} + o(1/n)$. Consequently, attaining any type of good (uniform)
efficiency with non-adaptive estimators will be challenging.

@@

We now consider a restricted case where each detection region is a
half-open interval, i.e., the $i$th message is obtained by comparing $X_i$
against a single threshold. Under the adaptive signal acquisition setting,
this is sufficient for asymptotic optimality;
in non-adaptive settings, it is not sufficient, though we may characterize
a few additional optimality results.
%% As we explain next, the existence of a density
%% for the sequence of thresholds is enough to establish local asymptotic
%% normality and leads to a closed-form expression for the precision parameter
%% and the ARE.
Assume now that each $B_i$ is of the form
\begin{equation}
  \label{eq:threshold_message}
  B_i = \sgn(t_i - X_i) = \begin{cases} 1 & X_i<  t_i, \\
    -1 & X_i \geq t_i,
  \end{cases}  
\end{equation}
where $t_i\in\mathbb R$ is the \emph{threshold} of the $i$th encoder. In
other words, the detection region of $B_i$ is $A_i = (t_i,\infty)$ and
$\mathbb P(X_i \in A_i) = F \left( B_i(t_i-\theta) \right)$. It follows that
\begin{equation}
  L_n(A_1,\ldots,A_n;\theta)
  = \frac{1}{n} \sum_{i=1}^n \frac{ \left(f(t_i-\theta) \right)^2 }{F\left(t_i-\theta \right) F\left(\theta - t_i \right) }  = \frac{1}{n} \sum_{i=1}^n \eta(t_i - \theta).
  \label{eq:Ln_threshold}
\end{equation}
A natural condition for the existence of the limit \eqref{eq:Ln_threshold}
as $n\to \infty$ is that the empirical distribution of the threshold values
converges to a probability measure. Specifically, for an interval $I \subset
\mathbb R$, define
\begin{equation*}
  \lambda_n(I) = \frac{ \card \left( I \cap \{t_1,t_2,\ldots \} \right)}{n}. 
\end{equation*}
Then an investigation of the proof of
Theorem~\ref{theorem:non-adaptive-minimax} in
Section~\ref{sec:proof-non-adaptive-minimax}, specifically
Sec.~\ref{sec:proof-lan-bits} and the bounds~\eqref{eqn:h-fourth}, show that
as $\eta(t) \le \eta(0)$ for all $t \in \R$ under
Assumption~\ref{assump:failure_rate}, the following corollary follows. (The
corollary relies on local asymptotic normality~\cite[Ch.~7]{VanDerVaart98};
see Appendix~\ref{sec:proof-sgd-regular} for some brief discussion of such
conditions.)
\begin{cor} \label{cor:LAN_thresh}
  Let $\{t_n\}_{n=1}^\infty$ be a sequence of threshold values such that
  $\lambda_n$ converges (weakly) to a probability measure $\lambda$ on
  $\mathbb R$. Then the conclusions of
  Theorem~\ref{theorem:non-adaptive-minimax} apply with
  %% $\left\{ B_i = \sgn(X_i - t_i) \right\}_{i=1}^n$ is a
  %% LAN family with precision parameter
  \begin{equation*}
    \kappa(\theta) = \int_{\mathbb R} \eta(t-\theta) \lambda(dt). 
  \end{equation*}
  Moreover, the family of laws of $\{B_i = \sgn(X_i - t_i)\}_{i = 1}^n$
  under $\{P_\theta\}_{\theta \in \Theta}$ is locally asymptotically normal
  with information $\kappa(\theta)$.
\end{cor}

@@

By Assumption~\ref{assump:failure_rate},
$\eta(x)$ attains its maximum at the origin, so we conclude that
\begin{equation*}
  \kappa(\theta) \leq \sup_{t\in \mathbb R} \eta \left( t-\theta\right) = \eta(0).
\end{equation*}
Moreover, this upper bound on $\kappa(\theta)$ is attained only when
$\lambda$ is the point mass at $\theta$. Since $\theta$ is \emph{a priori}
unknown, estimation in the distributed setting using
threshold detection is strictly suboptimal compared to the adaptive
setting; the ability to choose the thresholds $t_i$
adaptively conditional on previous messages is necessary for optimal
efficiency.

@@

\begin{figure}
  %%%%% COMMENTED TIKZ PICTURE %%%%%
  \begin{center}
\begin{tikzpicture}[scale = 1]
\begin{axis}[
width=8cm, height=6cm,
xmin=.03,
xmax=2.5, 
xmode = log,
restrict y to domain = 0:100,
ymin = 0,
ymax = 1,
samples=1, 
xlabel= {$\sigma$},
%xtick={-0.5,0,0.5},
%xticklabels={-$$, 0, $b$},
ytick={0,0.637,1},
yticklabels={0,$\frac{2}{\pi}$,1},
ylabel = {\scriptsize Relative Efficiency},
line width=1.0pt,
mark size=1.5pt,
ymajorgrids,
xmajorgrids,
legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
]
\addplot[color = red, smooth,
line width=1.0pt,
%mark size=1.5pt,mark=x,
] plot table [x = x, y = y, col sep=comma] {./Figs/minmax_ARE_b0.5.csv};
\addlegendentry{\scriptsize optimal threshold density};

\addplot[color = black!35!green, dashed, line width=1.0pt,
        %mark size=1.5pt, mark=^
        ]
 plot table [x = x, y = z, col sep=comma] {./Figs/minmax_ARE_b0.5.csv};
\addlegendentry{\scriptsize uniform threshold desnity};

\addplot[color = black, smooth, dotted, line width = 1pt] 
coordinates {
            (0.03, .637) (10, .637)
            };
\addlegendentry{\scriptsize attained in the adaptive case};
%\draw[->] (axis cs:0.1,.5) -- node[below, align=center] {\scriptsize ARE attained in \\ \scriptsize the adaptive case} (axis cs:0.1, .63);
\end{axis}
\end{tikzpicture}
\caption{\label{fig:minimax_ARE} 
Minimax relative efficiency under distributed encoding. ARE versus $\sigma$ for $f(x)$ the standard normal density with variance $\sigma^2$ and parameter space $\Theta = [-1/2,1/2]$. The dashed curve (green) is the ARE under a uniform threshold density over $\Theta$ given by $K_{\unif}\sigma^2$ of \eqref{eq:uniform_risk}. \newtext{
The line $\pi/2$ is attained under adaptive encoding uniformly over the parameter space for any $\sigma$.}}
\end{center}
\end{figure}
